Automated topic naming to support analysis of software maintenance activities

### 2010-08-19 icse/icse2011.tex
icse crud
more icse'in it up
fixing viz section

\usepackage{comment}
\newtheorem{mydef}{definition}
\usepackage{graphicx}
\newcommand{\slbl}[1]{\textbf{\textsf{#1}}}
\usepackage{multirow}%,multicolumn}
\usepackage{slashbox}
\usepackage{wrapfig}
\usepackage{booktabs, colortbl}
\usepackage{amsmath}
\usepackage[pdfstartview=FitH,bookmarksopenlevel=3,bookmarks=true]{hyperref} %pdfpagescrop={92 112 523 778},

\usepackage{url}
\begin{document}
\numberofauthors{5}
\author{
\alignauthor 
Abram Hindle\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{ahindle@uwaterloo.ca}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor Richard C. Holt \\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{holt@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

%\title{What's in a name? Automated topic naming of software maintenance activities}
\title{Automated topic naming to support analysis of software maintenance activities}
\maketitle
\thispagestyle{empty}

@@

Topics in software engineering practice refer to specific `threads' between project stakeholders. These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
In addressing a topic of development stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed).
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.
The goal of concept location and topic analysis research is to recover these topics and the related software artifacts.
% get neil's data mining point in there
To date, the results of topic analysis and concept location are project specific, and not globally generalizable.
% get the interpretation aspect
Much of the current research stops short of interpreting the purpose of the topic. That is, extracted topics are usually manually named and labelled by those who read the topic words.
% 
In this paper we propose a method of interpreting and labelling topics, and their related artifacts, that is generalizable and relevant to multiple projects.

@@

In multi-label learning the technique can perform micro or macro measurements. Macro measurements are aggregated at a class or label level. Micro measurements are aggregated at a decision level. So a macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. Unfortunately for MaxDB, the macro-ROC values are undefined because of poor performance of one of the labels.

@@

\subsection{Visualization}
We created two visualizations of the manually labelled data. A problem we faced while visualizing was how to display tag overlaps. Our solution, while not optimal, was to assign a separate colour to each distinct set of annotations. Figures \ref{fig:maxdb} and \ref{fig:mysql} show extracted topics grouped by annotations. Annotations or labels that occur in adjacent windows are joined together as trends. For MaxDB (Figure \ref{fig:maxdb}) the largest trends were related to maintainability and portability. MaxDB supports numerous platforms and portability was a constant issue facing the project's development. MySQL was different, with many topics overlapping, so there were many different subsets. Functionality trends were prevalent throughout its history (the largest reddish streak across the top). Two combination  tags of ``functionality portability'' (orange) and ``maintainability portability'' (teal) streaked across most of the history of MySQL. Since this was MySQL 3.23, a stable branch, we expect that issues dealing with portability and maintenance would be the primary concerns of this branch: developers probably wanted it to work with current systems and thus had to update it.

@@

\begin{figure*}[ht]
\centering
\subfigure[MaxDB 7.500]{
\includegraphics[width=\textwidth]{figures/maxdb-timeline-all}
\label{fig:mysql-timeline}
}
\subfigure[MySQL 3.23]{
\includegraphics[width=\textwidth]{figures/mysql-timeline-all}
\label{fig:maxdb-timeline}
}
\label{fig:timelines}
\caption[]{NFRs over time. Numbers represent topics labelled with that quality. Box intensity (saturation) is mapped to label frequency relative to the largest label value.
\todo[inline]{better discussion}
}
\end{figure*}

@@

% What did we do
% What did we show
% What did we do that was new?

% use domain knowledge
We demonstrated that static but domain-specific knowledge can improve unsupervised labelling of extracted topics. 
Our \textsf{exp2} experiment used small accurate word bags to label topics but performed just as well as \textsf{exp3}, which used many more general terms from WordNet.
We then showed that with some supervision, and by using efficient machine learners based on Naive Bayesian classifiers, we could improve the accuracy of automatic labelling topics even further.

>>>>

\usepackage{comment}
\newtheorem{mydef}{definition}
\usepackage{graphicx}
\newcommand{\slbl}[1]{\textbf{\textsf{#1}}}
\usepackage{multirow}%,multicolumn}
\usepackage{slashbox}
\usepackage{wrapfig}
\usepackage{booktabs, colortbl}
\usepackage{amsmath}
\usepackage{url}
\usepackage[pdfstartview=FitH,bookmarksopenlevel=3,bookmarks=true]{hyperref} %pdfpagescrop={92 112 523 778},

\begin{document}
\numberofauthors{5}
\author{
\alignauthor 
Abram Hindle\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{ahindle@uwaterloo.ca}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor Richard C. Holt \\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{holt@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

%\title{What's in a name? Automated topic naming of software maintenance activities}
\title{Automated topic naming to support analysis of software maintenance activities}
\maketitle
%\thispagestyle{empty}

@@

Topics in software engineering practice refer to specific `threads' between project participants. These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'participants' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
In addressing a topic of development participants often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed).
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.
The goal of concept location and topic analysis research is to recover these topics and the related software artifacts.
% get neil's data mining point in there
To date, the results of topic analysis and concept location are project specific, and not globally generalizable.
% get the interpretation aspect
Much of the current research stops short of interpreting the purpose of the topic. That is, extracted topics are usually manually named and labelled by those who read the topic words.
% 
In this paper we propose a method of interpreting and labelling topics, and their related artifacts, that is generalizable and relevant to multiple projects.

@@

In multi-label learning the technique can perform micro or macro measurements. Macro measurements are aggregated at a class or label level. Micro measurements are aggregated at a decision level. \todo[inline]{this is unclear, could do with a few more sentence explaining why we should care.}
 So a macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. Unfortunately for MaxDB, the macro-ROC values are undefined because of poor performance of one of the labels.

@@

\subsection{Visualizations}
Figures \ref{fig:maxdb-timeline} and \ref{fig:mysql-timeline} show the temporal patterns of label frequencies. There are two measures represented. One, the relative frequency, shown in the grey boxes, represents the number of labels with that NFR in that period, relative to the maximum number of topics assigned to that NFR. The second, absolute frequency, compares the number of topics labelled with that NFR per period relative to the maximum number of labelled topics overall.

For example, in Fig. \ref{fig:mysql-timeline}, we see that the NFRs functionality, portability and maintainability contain more labeled topics, since these NFRs have more intense shaded boxes.

% For MaxDB (Figure \ref{fig:maxdb}) the largest trends were related to maintainability and portability. MaxDB supports numerous platforms and portability was a constant issue facing the project's development. MySQL was different, with many topics overlapping, so there were many different subsets. Functionality trends were prevalent throughout its history (the largest reddish streak across the top). Two combination  tags of ``functionality portability'' (orange) and ``maintainability portability'' (teal) streaked across most of the history of MySQL. Since this was MySQL 3.23, a stable branch, we expect that issues dealing with portability and maintenance would be the primary concerns of this branch: developers probably wanted it to work with current systems and thus had to update it.

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL 3.23]{
\includegraphics[width=\textwidth]{figures/mysql-timeline}
\label{fig:maxdb-timeline}                               
}                                                        
\subfigure[MaxDB 7.500]{                                 
\includegraphics[width=\textwidth]{figures/maxdb-timeline}
\label{fig:mysql-timeline}
}
\label{fig:timelines}
\caption[]{NFR label per period. Each box represents a 30-day period. Numbers represent number of topics in that period labelled with that NFR. Box intensity (saturation) is mapped to label frequency relative to the largest label value of \emph{all} NFRs. Grey bars indicate label frequency relative to \emph{that} NFR.
\todo[inline]{better discussion}
}
\end{figure*}

@@

We demonstrated that static but domain-specific knowledge can improve unsupervised labelling of extracted topics. Our \textsf{exp2} experiment used small accurate word bags to label topics but performed just as well as \textsf{exp3}, which used many more general terms from WordNet. We then showed that with some supervision, and by using efficient machine learners based on Naive Bayesian classifiers, we could improve the accuracy of automatic labelling topics even further.
